CommonMind Consortium: DLPFC

### 2020-09-21 combined_analysis/diff.networks.Rmd
Update diff networks

# Null permuations
```{r diff.networks.perm}

@@

	# Discover clusters in first cohort
	#----------------------------------
	C = diff.net[[1]]
	C.diff.discovery = C[[2]] - C[[1]]
	C.diff.discovery = C.diff.discovery[[1]][keep.ensID,keep.ensID]

@@

```{r perm.results, fig.width=5}
p = df_test$P.Value[df_test$Cohort=="MSSM-Penn-Pitt"]
# print(1 - qvalue(p)$pi0)
hist(p, main="P-values under the null in the discovery cohort", xlab="p-value")

@@

# Null network
```{r diff.networks.null}

@@

# Discover clusters in first cohort
#----------------------------------
C = diff.net[[1]]
C.diff.discovery = C[[2]] - C[[1]]
C.diff.discovery = C.diff.discovery[[1]][keep.ensID,keep.ensID]

@@

ggplot(res, aes(Power, -sign(slope)*SFT.R.sq, color=paste(Cohort, Dataset, sep=' - '))) + geom_point() + theme_bw() + theme(aspect.ratio=1,  plot.title = element_text(hjust = 0.5)) + xlab(="Soft Threshold (power)") + ylab("Scale Free Topology Model Fit,signed R^2") + ggtitle("Scale independence")

# Discover clusters in first cohort
#----------------------------------
C = diff.net[[1]]
C.diff.discovery = C[[2]] - C[[1]]
C.diff.discovery = C.diff.discovery[[1]][keep.ensID,keep.ensID]

@@

df_sft = pickSFT( diff.net.Sex )

@@

# Discover clusters in first cohort
#----------------------------------
C.diff.discovery = diff.net.Dx[[1]][keep.ensID,keep.ensID]

@@

@@

# Discover clusters in first cohort
#----------------------------------
C = net.Dx_Sex[[1]]
C.diff.discovery = (C[[lvls[4]]] - C[[lvls[3]]]) - (C[[lvls[2]]] - C[[lvls[1]]])

>>>>

# Null permuations
```{r diff.networks.perm, eval=FALSE}

@@

	pwr = 7

	# Discover clusters in first cohort
	#----------------------------------
	C = diff.net[[1]]
	C.diff.discovery = C[[2]]^pwr - C[[1]]^pwr
	C.diff.discovery = C.diff.discovery[keep.ensID,keep.ensID]

@@

```{r perm.results, fig.width=5, eval=FALSE}
p = df_test$P.Value[df_test$Cohort=="MSSM-Penn-Pitt"]
# print(1 - qvalue(p)$pi0)
hist(p, main="P-values under the null in the discovery cohort", xlab="p-value")

@@

# Null network
```{r diff.networks.null, eval=FALSE}

@@

# Discover clusters in first cohort
#----------------------------------
C = diff.net[[1]]
C.diff.discovery = C[[2]]^pwr - C[[1]]^pwr
C.diff.discovery = C.diff.discovery[keep.ensID,keep.ensID]

@@

ggplot(res, aes(Power, -sign(slope)*SFT.R.sq, color=paste(Cohort, Dataset, sep=' - '))) + geom_point() + theme_bw() + theme(aspect.ratio=1,  plot.title = element_text(hjust = 0.5)) + xlab("Soft Threshold (power)") + ylab("Scale Free Topology Model Fit,signed R^2") + ggtitle("Scale independence")

# Discover clusters in first cohort
#----------------------------------
C = diff.net[[1]]
C.diff.discovery = C[[2]]^pwr - C[[1]]^pwr
C.diff.discovery = C.diff.discovery[keep.ensID,keep.ensID]

@@

@@

res = pickSFT( diff.net.Dx )

ggplot(res, aes(Power, -sign(slope)*SFT.R.sq, color=paste(Cohort, Dataset, sep=' - '))) + geom_point() + theme_bw() + theme(aspect.ratio=1,  plot.title = element_text(hjust = 0.5)) + xlab("Soft Threshold (power)") + ylab("Scale Free Topology Model Fit,signed R^2") + ggtitle("Scale independence")

# Discover clusters in first cohort
#----------------------------------

C = diff.net[[1]]
C.diff.discovery = C[[2]]^pwr - C[[1]]^pwr
C.diff.discovery = C.diff.discovery[keep.ensID,keep.ensID]

@@

res = pickSFT( net.Dx_Sex )

ggplot(res, aes(Power, -sign(slope)*SFT.R.sq, color=paste(Cohort, Dataset, sep=' - '))) + geom_point() + theme_bw() + theme(aspect.ratio=1,  plot.title = element_text(hjust = 0.5)) + xlab("Soft Threshold (power)") + ylab("Scale Free Topology Model Fit,signed R^2") + ggtitle("Scale independence")

pwr = 7

@@

# Discover clusters in first cohort
#----------------------------------
C = net.Dx_Sex[[1]]
C.diff.discovery = (C[[lvls[4]]]^pwr - C[[lvls[3]]]^pwr) - (C[[lvls[2]]]^pwr - C[[lvls[1]]]^pwr)
